---
# title: "Team Lead Proposal"
# author: 
#   - name: Tony Liang
#   - name: Jeffrey Tang
#   - name: Aditi Srinivasan

date: 2024-01-29
engine: knitr
format: 
  revealjs:
    slide-number: true
    # serif looks very similar to lead but ugly
    # night is also good?
    width: 1600
    height: 900
    theme: [default, custom.scss]
    css: custom.css
    hash-one-based-index: true
    embed-resources: true
    mouse-wheel: true
    code-overflow: wrap
    lang: en-CA
    output-file: index.html
    transition: fade
editor: source
---

```{r}
#| label: setup
#| warning: false
#| message: false

library(dplyr)
library(magrittr)
```

# {.winter}


::: {.title}

Team Lead Proposal

:::

<br>


::: {.center-text .smaller}

Tony Liang, Jeffrey Tang, Aditi Srinivasan
:::

::: {.center-text}
University of British Columbia
:::

::: {.center-text}
2024-01-29
:::


## Background {.winter}

- What is already known in context of this study

::: {.callout-note}
# Test the note

Use this to highlight something?

:::

## Question/Hypothesis {.winter}

- What is the knowledge gap you are trying to fill?
- What do you expect to find?


::: {.callout-tip}

Use this as a tip

:::


## Data Source {.winter .scrollable}


- Describe content and source of the data you will use?

- If using previously published data, how will your project differ from previous literature?



```{r}
#| label: tbl-dataset
#| echo: false
#| tbl-cap: "Dataset to benchmark from GEO, and metadata"
sample_path <- here::here("data/sample_data.csv")
col_names <- c("GSE ID", "Data Type", "Healthy/Cancer", "Number of patients", "Number of cells", "Sequencing platform", "Cell level annotation availablity")
df <- read.csv(sample_path)
df %>% knitr::kable(col.names = col_names,
                    align='llccccr')

```

::: {.notes}

- Note 1 
- Note 2
- Note 3

:::


## Analysis Plan {.winter}

- How will you answer your main research question?


## {.winter}


Questions ?